\scuba: iterative map-making with the Sub-Millimetre User Reduction Facility

### 2012-08-24 smurf_paper.tex
minor fiddle in intro

In this section we summarize how \scuba\ bolometers detect temperature
variations (Section~\ref{sec:bolos}), describe \scuba\ scan strategies
(Section~\ref{sec:scan}), typical bolometers signals
(Section~\ref{sec:bolosignal}), and the impact of magnetic field
pickup (Section~\ref{sec:magpickup}, describe the differences between
SCUBA-2 Shared Risk Observing data and those of the the fully
commissioned instrument (Section~\ref{sec:s2sro}), and finally
illustrate the use of principal component analysis
(Section~\ref{sec:pca}).

>>>>

In this section we summarize how \scuba\ bolometers detect temperature
variations (Section~\ref{sec:bolos}), describe \scuba\ scan strategies
(Section~\ref{sec:scan}), describe the differences between SCUBA-2
Shared Risk Observing data and those of the the fully commissioned
instrument (Section~\ref{sec:s2sro}), typical bolometers signals
(Section~\ref{sec:bolosignal}), the impact of magnetic field pickup
(Section~\ref{sec:magpickup}, and finally illustrate the use of
principal component analysis (Section~\ref{sec:pca}).
